### 2017-04-06 paper/evaluation.tex
first par. rq5

To understand why developers prefer not use parallel test execution,
we considered \numNonParallel{} subjects that do not use parallel
configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the 
\numNonParallel{} projects, and we did not found any e-mail from
\Fix{??} projects using \CodeIn{git} tool.
\Luis{Here I want to say that I could not found any valid e-mail using
\textit{git log}}
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
projects, and \emailsFalseAnswers{} developers was not able to 
explain how the testing works or was not able to answer the survey.

>>>>

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \Fix{y} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails to those developers with the survey.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.

\Mar{----- estou aqui}
